BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for Realistic BPMN Models

### 2024-07-31 paper.tex
Merge related work and maturity

% Paper structure
In the remainder of the paper, we describe how instantaneous, comprehensible, and fixable control flow error detection is achieved in \autoref{sec:innovations}.
Then, we discuss the maturity of our tool in \autoref{sec:maturity} before presenting related work in \autoref{sec:related-work}.
Finally, we conclude in \autoref{sec:conclusion}.

@@

\section{Maturity of the Tool} \label{sec:maturity}
The BPMN Analyzer is our newest tool, incorporating many findings from our previous work~\cite{krauterHigherorderTransformationApproach2024} while focusing on instantaneous and understandable error detectionn, as described in the previous section.
The tool is open source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aimed to achieve high code quality by employing industry best practices such as rigorous static analysis, testing, and consistent formatting.
Furthermore, we demonstrated the tool to companies in the BPMN process orchestration space and received positive feedback~\cite{krauterInstantaneousComprehensibleFixable2024}.

\section{Related Work} \label{sec:related-work}

@@

Our tool focuses on \textit{instantaneous} control flow analysis and does not support custom properties, data, or time.
We do not provide BPMN simulation since other tools already offer this.
However, we use token-flow animation to visualize control flow errors interactively.
This improves comprehension compared to previous static, less interactive visualizations.
In addition, to the best of our knowledge, our tool is the only one that provides \textit{quick fixes}, i.e., automatic resolutions if control flow errors are detected.
To sum up, our tool incorporates and enhances several ideas from the state of the art while adding novel concepts, such as quick fixes.
We advocate for a pragmatic approach, prioritizing performance and understanding above all else to ensure seamless integration into BPMN modeling tools.

>>>>

% Paper structure
In the remainder of the paper, we describe how instantaneous, comprehensible, and fixable control flow error detection is achieved in \autoref{sec:innovations}.
Then, we discuss related work and tool maturity in \autoref{sec:related-work} before concluding in \autoref{sec:conclusion}.

@@

\section{Related Work \& Maturity of the Tool} \label{sec:related-work}

@@

The BPMN Analyzer is our newest tool, which incorporates and enhances several ideas from the state of the art and focuses on instantaneous control flow analysis.
The tool is open source~\cite{krauterInstantaneousComprehensibleFixable2024}, and we aimed to achieve high code quality by employing industry best practices such as rigorous static analysis, testing, and consistent formatting.
Furthermore, we received positive feedbacked from companies in the BPMN process orchestration space~\cite{krauterInstantaneousComprehensibleFixable2024}.
We use token-flow animation to visualize control flow errors interactively, which improves comprehension compared to previous, non-interactive visualizations.
In addition, to the best of our knowledge, the tool is the only one that provides \textit{quick fixes}, i.e., automatic resolutions if control flow errors are detected.
We advocate for a pragmatic approach, prioritizing performance and understanding above all else to ensure seamless integration into BPMN modeling tools.
